### 2024-02-06 docs/projects/noj/ggplot.qmd
Noj - rerendered

<g id="surface679">

@@

## Representing plots as Clojure data
Inspired by
[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list finction, let us represent ggplot objects as R data structures.
A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.

>>>>

<g id="surface931">

@@

## Representing plots as Clojure data
A ggplot object is an R list of [ggproto](https://bookdown.dongzhuoer.com/hadley/ggplot2-book/introducing-ggproto) objects. We recursively unwrap this structure and convert it to Clojure.

### 2024-02-06 docs/projects/noj/ml.qmd
Noj - rerendered

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8799     -0.2284      0.0138      0.2569      0.6354

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.9687     0.3043     6.4705     0.0000 ***
sepal-width         0.6222     0.0800     7.7748     0.0000 ***
petal-length        0.6929     0.0713     9.7167     0.0000 ***
petal-width        -0.5072     0.1639    -3.0944     0.0026 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3196 on 96 degrees of freedom
Multiple R-squared: 0.8577,    Adjusted R-squared: 0.8533
F-statistic: 192.9066 on 4 and 96 DF,  p-value: 1.640e-40

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7855     -0.2024      0.0281      0.2007      0.6159

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.8316     0.3045     6.0143     0.0000 ***
sepal-width         0.6567     0.0798     8.2255     0.0000 ***
petal-length        0.6798     0.0680     9.9990     0.0000 ***
petal-width        -0.4501     0.1530    -2.9415     0.0041 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.2950 on 96 degrees of freedom
Multiple R-squared: 0.8767,    Adjusted R-squared: 0.8728
F-statistic: 227.5000 on 4 and 96 DF,  p-value: 1.726e-43
